\cvsection{Projects}

\begin{cventries}

  \cventry
  {The Lunchbox - Unified Platform for payments and ordering food \textbf{\{PHP, MySQL, JS\}}}
  {Summer Of Code by Nutanix and Govt. of UP}
  {IIT Kanpur}
  {May 2018-July 2018}
  {
    \begin{cvitems}
     \item Actively Contributed as a Full Stack developer with a team of 5 people, creating a platform, primarily aimed at promoting transparency in canteen bills and providing way to keep track of expenses(for customers) and sales stats(for canteens). 
     \item Implemented \textbf{canteen recommendation algorithm} which compares prices among all the vendors and also shows the order backlog for each canteen thereby suggesting the most convenient place for users to eat. 
     \item Implemented \textbf{food recommendation algorithm} which compares food items based on parameters like rating, price, etc.
     \item Promoted transparency by giving access to customers to see their order history at any date or in a given interval of time. 
     \item Used Prepared statements to prevent the site from SQL injection.
    \end{cvitems}
  }

  \cventry
  {Association of Computing Activities}
  {BFS}
  {IIT kanpur}
  {Feb,2017 - June,2017}
  {
     \begin{cvitems}
      \item Learned basics of BASH, Cryptography and Machine Learning.
      \item Done assignments in BASH using sed, grep, awk command.
      \item Built a \textbf{Movie Review Categoriser} using Naive Bayes Classifier Technique
            to classify reviews into positive or negative\\ with an estimated accuracy of \textbf{75.1\%} on the test data.
     \end{cvitems}
  }

  \cventry 
  {Manufacturing Processes}
  {Foldable Fussball Table}
  {IIT Kanpur}
  {Aug,2018 - Nov,2018}
  {
    \begin{cvitems}
      \item Designed a Fussball table which can be folded in the form of Briefcase.
      \item Compiled a 3D model on AutoCAD and Fusion360 of our project along with various part drawings.
      \item Wrote project report containing the material required,Parts to be made and Work distribution.
    \end{cvitems}
  }

  \cventry
  {To learn new concepts}
  {Self-Projects}
  {}
  {}
  {
    \begin{cvitems}
      \item Shell Script - Created a file searching command in BASH using Recursion in file tree.
      \item Nodejs - Created a CLI to access data related to NSE stocks in javascript.
      \item Nodejs - Build a REST Api to perform CRUD operation.
      \item Nodejs - Build a web scraper to scrape the codechef contest details.   
    \end{cvitems}
  }
\end{cventries}

%%% Local Variables:
%%% mode: latex
%%% End:
